---
title: "eds212-day4-task"
---

## End of day task

```{r}
library(tidyverse)
library(skimr)
library(GGally)

```

## **Data exploration & summarizing in R**

-   Create a new Project

-   Add a new Quarto document in your project, save as `r-exploring`

-   Set up your local and remote git repo by running `usethis::use_git()` and then `usethis::use_github()`

-   Attach the `tidyverse`, `skimr`, and `GGally` packages in the setup code chunk

-   Run `View(diamonds)` in the Console to look at the built-in `diamonds` dataset in R

-   Explore the dataset using the functions `names()`, `dim()`, `summary()`, `head()`, `tail()`, and `skimr::skim()`

-   Create a pairs plot using `ggpairs()`

-   Create a basic `ggplot` scatterplot of diamond price (`price`) as a function of size (`carat`)

-   Create a histogram showing the distribution of values in the `carat` column (recall: a histogram only requires a single variable, e.g. `aes(x = carat)`)

-   Save, stage, commit, pull, then push your changes back to your repo in RStudio **using the GUI interface (buttons)**

-   Create a boxplot (see: `geom_box`) of diamond clarity (on the x-axis) and price (y-axis).

-   **In the command line**, stage, commit, & push changes

## 

## Exploring data

```{r}
names(diamonds)
```

```{r}
dim(diamonds)
```

```{r}
summary(diamonds)
```

```{r}
head(diamonds)
```

```{r}
tail(diamonds)
```

```{r}
skimr::skim(diamonds)
```

```{r}
ggpairs(diamonds)
```

```{r}
ggplot(data = diamonds, aes(x = carat, 
                            y = price)) +
  geom_point(aes(color = cut))
```

```{r}
ggplot(data = diamonds, aes(x = carat)) +
  geom_histogram(aes(fill = cut)) + 
  theme_minimal() 
```
